Exploring the role of electric field in the catalase active site

### 2018-03-10 bb494/manuscript.tex

@@

>>>>

\textbf{pH-dependent assay}
pH assays were conducted using the same kinetic method described above. Reactions occured in 3mL equilibration buffer (50mM sodium phosphate, 300mM NaCl, 5\% $H_2O_2$ pH modulated to values from 5 to 10 via addition of HCL or NaOH). On addition of 43$\mu g$ protein, the tubes were mixed and incubated at RT for five minutes, then brought to 5\% $H_2O_2$ and added to pressure assay mechanism. Trials were conducted in triplicate.\\

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}{\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
    \begin{minipage}{0.9\textwidth}\includegraphics[width=0.9\linewidth]{figures/kinetics.png}\end{minipage}
  \end{subfigure}
  \caption{\textbf{Michaelis-Menten plot of kinetic efficiencies of HPII variants.} Kinetic measurements conducted at 25C using the pressure-based assay defined above.}
\label{fig:kinetics}
\end{figure}

\begin{figure}[h!]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
    \begin{minipage}{0.9\textwidth}\includegraphics[width=0.9\linewidth]{figures/wildtype-velocity.png}\end{minipage}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
    \begin{minipage}{0.9\textwidth}\includegraphics[width=0.9\linewidth]{figures/3ny-velocity.png}\end{minipage}
  \end{subfigure}
  \caption{\textbf{pH dependent initial velocities of HPII variants.} Left: HPII catalase Right: HPII-3NY.}
\label{fig:ph-dependent-velocities}
\end{figure}
